### 2014-03-05 src/methodology.Rnw
update

<<opstable,results='asis'>>=
op=c(
'INVERT-NEGS',
'RETURN-VALS',
'MATH',
'VOID-M-CALLS',
'NEGATE-COND',
'COND-BOUNDARY',
'INCREMENTS',
'NVOID-M-CALLS',
'CONSTR-CALLS',
'INLINE-CONSTS',
'RM-INCR',
'E-MEMBER-VAR',
'E-SWITCH',
'RM-SWITCH',
'RM-COND',
'DELETE-COND')
expl=c(
'Invert negatives',
'Change return values',
'Modify arithmetic operators',
'Remove void method calls',
'Negate conditional statements',
'Modify boundary conditions',
'Modify increment/decrement',
'Replace non-void method calls',
'Replace constructor calls',
'Replace inline constants',
'Remove increment/decrement',
'Replace member variable assignments',
'Modify switch statements',
'Remove switch elements*',
'Make conditionas true',
'Make conditionas false*')
op.df <- data.frame(Operator=op, Explanation=expl)
print(xtable(op.df,caption='PIT Mutation Opeators (* indicates new opeators)', label='table:pitop'), sanitize.text.function  = function(x){x}, include.colnames=FALSE, include.rownames=F)
@

>>>>

<<opstable,results='asis'>>=
op=c(
'INVERT-NEGS',
'RETURN-VALS',
'MATH',
'VOID-M-CALLS',
'NEGATE-COND',
'COND-BOUNDARY',
'INCREMENTS',
'NVOID-M-CALLS',
'CONSTR-CALLS',
'INLINE-CONSTS',
'RM-INCR',
'E-MEMBER-VAR',
'E-SWITCH',
'RM-SWITCH',
'RM-COND',
'DELETE-COND')
expl=c(
'Invert negatives',
'Change return values',
'Modify arithmetic operators',
'Remove void method calls',
'Negate conditional statements',
'Modify boundary conditions',
'Modify increment/decrement',
'Replace non-void method calls',
'Replace constructor calls',
'Replace inline constants',
'Remove increment/decrement',
'Replace member variable assignments',
'Modify switch statements',
'Remove switch elements*',
'Make conditionas true',
'Make conditionas false*')
op.df <- data.frame(Operator=op, Explanation=expl)
print(xtable(op.df,caption='PIT Mutation Opeators (* indicates new opeators)', label='tbl:pitop'), sanitize.text.function  = function(x){x}, include.colnames=FALSE, include.rownames=F)
@

### 2014-03-05 src/paper.Rnw
update

% 10 pages for the main text + 1 for references.
<<>>=
data(o.dist.all)
data(o.dist.det)
data(r.dist.all)
data(r.dist.det)
@
\input{intro}

\input{related}
\input{methodology}
\input{analysis}

\subsection{Operators}

@@

\subsection{SDL vs Random selection}
\begin{figure*}[t]
<<sdl.1,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
par(mfrow=c(2,2))
with(o.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Original SDL'))
with(o.pit.all, plot(all.cov~x1_per_line.cov, pch='+', main='Original 1 per line'))
with(r.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Randoop SDl'))
with(r.pit.all, plot(all.cov~x1_per_line.cov, pch='+', main='Randoop 1 per line'))
@
\label{fig:sdl1}
\caption{Statement Deletion vs One per line.}
\end{figure*}

<<results='asis'>>=
o <- subset(stats.df, kind == 'original')
o.x <- subset(o, select=c('operator', 'r.square', 'mutant.reduction', 'sample', 'score.multiplier'))
colnames(o.x) <- c('operator', 'r^2', 'm.red', 'sample', 'mcov.mult')
print(xtable(o.x, caption='Original', label='table:try1'), include.rownames=FALSE)
# , sanitize.text.function = function(x){x}, include.rownames=FALSE)
@
<<results='asis'>>=
r <- subset(stats.df, kind == 'randoop')
r.x <- subset(r, select=c('operator','r.square', 'mutant.reduction', 'sample', 'score.multiplier'))
colnames(r.x) <- c('operator', 'r^2', 'm.red', 'sample', 'mcov.mult')
print(xtable(r.x, caption='Randoop', label='table:try1'), include.rownames=FALSE)
@

@@

>>>>

% 10 pages for the main text + 1 for references.
<<>>=
data(o.dist.all)
data(o.dist.det)
data(r.dist.all)
data(r.dist.det)
@
<<test, child='intro.Rnw'>>=
@
<<test, child='related.Rnw'>>=
@
<<test, child='methodology.Rnw'>>=
@
<<test, child='analysis.Rnw'>>=
@

@@

\subsection{SDL vs Random selection}
\begin{figure*}[t]
<<sdl.1,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
par(mfrow=c(2,2))
with(o.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Original SDL'))
with(o.pit.all, plot(all.cov~x1_per_line.cov, pch='+', main='Original 1 per line'))
with(r.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Randoop SDl'))
with(r.pit.all, plot(all.cov~x1_per_line.cov, pch='+', main='Randoop 1 per line'))
@
\label{fig:sdl1}
\caption{Statement Deletion vs One per line.}
\end{figure*}
<<results='asis'>>=
o <- subset(stats.df, kind == 'original')
o.x <- subset(o, select=c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
colnames(o.x) <- c('operator', 'r^2', 'm.red', 'm.sd', 'num', 'B*')
print(xtable(o.x, caption='Original', label='table:try1'), include.rownames=FALSE)
# , sanitize.text.function = function(x){x}, include.rownames=FALSE)
@
<<results='asis'>>=
r <- subset(stats.df, kind == 'randoop')
r.x <- subset(r, select=c('operator','r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
colnames(r.x) <- c('operator', 'r^2', 'm.red','m.sd', 'num', 'B*')
print(xtable(r.x, caption='Randoop', label='table:try1'), include.rownames=FALSE)
@

@@

\begin{figure*}[t]
\includegraphics[totalheight=6cm]{fig/original.pdf}
\caption{Subsumption Original}
\label{fig:subsumptiono}
\end{figure*}[t]

\begin{figure*}[t]
\includegraphics[totalheight=6cm]{fig/randoop.pdf}
\caption{Subsumption Randoop}
\label{fig:subsumptionr}
\end{figure*}[t]
